No Title

### 2017-10-26 paper/paper.tex
inertia tensor

@@

From this tensor we compute its eigenvalues,
$\lambda_1>\lambda_2>\lambda_3$, and corresponding eigenvectors,
$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
We define the size of its three ellipsoidal axis as
$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.

We define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
planar satellite distribution. 
We also define the width of the planar satellite distribution,
$\sigma_p$ as the standard deviation of all satellite distances to the
plane defined by the $\hat{n}$.

We characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies as $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$. 
It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web.

\subsection{Parameter Distributions}

We charaterize the $\mu$ distribution by a power law probability
density distribution
\begin{equation}
P(\mu) = \frac{1}{\alpha}\mu^{\alpha-1}.
\end{equation}
We estimate the $\alpha$ using a bayesian approach, such as that
the likelihood of being $\alpha$ the power value given the observed values of $\{\mu_i\}$
  can be written as:

\begin{equation}
\mathcal{L}(\alpha|\{\mu_i\})=\frac{1}{Z_\alpha}\prod_{i=1}^{N_s}
\frac{1}{\alpha}\mu_i^{\alpha-1}, 
\end{equation}
%
where $Z_{\alpha}$ is a constant such as $\int_{0}^{\infty}
{\mathcal L}(\alpha|\{\mu_i\}) {\rm d}\alpha=1$. 
We report as $\hat{\alpha}$ the value of $\alpha$ 
maximizing the likelihood,

We characterize the distributions for the plane width and axis ratio
$b/a$, $b/c$ through a gaussian
\begin{equation}
P(x)  = \frac{1}{\sqrt{2\pi \sigma^2}} \exp{\left[-\frac{1}{2}\left(\frac{x-x_m}{\sigma}\right)^2\right]}
\end{equation}
In this case the maximum likelihood values for the parameter estimates
$\hat{x_m}$ and $\hat{\sigma}$ correspond to the mean and standard
deviation, respectively.

We summarize the results from the Illustris simulation by reporting
the maximum likelihood parameter estimates. 
In turn we use this us to estimate the probability of finding the
observed values in the Local Group and compare it against the highest
probabilty values.

>>>>

It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web.

@@

From this tensor we compute its eigenvalues,
$\lambda_1>\lambda_2>\lambda_3$, and corresponding eigenvectors,
$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
We define the size of the three ellipsoidal axis as
$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
We also define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
planar satellite distribution. 
We also define the width, $w$, of the planar satellite distribution,
$\sigma_p$ as the standard deviation of all satellite distances to the
plane defined by the vector $\hat{n}$. 
Finally, we characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$.

To summarize we characterize the satellite distribution by for
quantities obtained from the inertia tensor: 
\begin{itemize}
\item Plane width, $w$.
\item $c/a$ axis ratio.
\item $b/a$ axis ratio.
\item $\mu$ as a measure of plane alignment.
\end{itemize}
